Combining information from photometric and spectroscopic data:\\ Don't waste your time in spectrophotometric calibration!

### 2014-08-04 tex/ms.tex
alternative GP formulation rewrite, cal figures for this alternative

>>>>

XXX Alternative XXX.
Because the residual column vector $\Delta$ of equation
\ref{eq:spectroscopicLF} is additive with respect to the mean model
$\mu$, sharp spectral features in the mean model (such as absorption
lines) can be artificially
diluted or enhanced, affecting the derived parameters. To mitigate this we construct a
model where the residual column vector is taken to be the residual
\emph{from the calibration vector $f(\alpha)$} and is multiplicative
with respect to the mean model $\mu$.  That is,
\begin{eqnarray}\label{eq:spectroscopicLFalt} \Delta &\equiv&
\frac{d}{\mu(\theta)} - f(\alpha) \quad ,
\end{eqnarray}
where $d$, $\mu(\theta)$ and $f(\alpha)$ are as before.
